---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# christinehoogland

<!-- badges: start -->
<!-- badges: end -->

The goal of christinehoogland is to practice package creation

## Installation

You can install the development version of christinehoogland from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("choogland/christinehoogland.pkg")
```

or locally with:
``` r
remotes::install_local(path = 'christinehoogland_0.0.0.9000.tar.gz')
```

# Function bmi

This function returns the Body Mass Index of an individual (https://en.wikipedia.org/wiki/Body_mass_index).

The function must take 2 parameters, the mass in kg and the height in meter. It returns the result of the operation mass/(height * height).


```{r examples-bmi}
bmi(mass = 80, height = 1.80)
bmi(mass = NA, height = 1.80)
bmi(mass = 80, height = NA)
bmi(mass = NA, height = NA)
```



## Code of Conduct
  
  Please note that the christinehoogland project is released with a [Contributor Code of Conduct](https://contributor-covenant.org/version/2/0/CODE_OF_CONDUCT.html). By contributing to this project, you agree to abide by its terms.
