---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# christinehoogland

<!-- badges: start -->
<!-- badges: end -->

The goal of christinehoogland is to practice package creation

## Installation

You can install the development version of christinehoogland like so:

``` r
# install.packages("devtools")
devtools::install_github("choogland/christinehoogland")
```

## Function bmi

# This line works:

```{r example-ok}
library(christinehoogland)

bmi(mass = 80, height = 1.80)
bmi(mass = NA, height = 1.80)
bmi(mass = 80, height = NA)
bmi(mass = NA, height = NA)

```



## Code of Conduct
  
  Please note that the christinehoogland project is released with a [Contributor Code of Conduct](https://contributor-covenant.org/version/2/0/CODE_OF_CONDUCT.html). By contributing to this project, you agree to abide by its terms.
